A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-03 mt-marathon.2013/PBML_article.tex
more
Glue comparison

%% Sample file $Id: PBML_article.tex 134 2010-07-01 19:28:04Z popel $
\documentclass{pbml}
%\documentclass[nofonts]{pbml} % for XeLaTeX without Pagella and DejaVu fonts
%\documentclass[color]{pbml} % for color images and hypertext links

@@

Secondly, the glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
\begin{verbatim}
   S -> <s>
   S -> S X
   GOAL -> S </s> 
\end{verbatim}
where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
\begin{verbatim}
   S -> X
   S -> S X
   GOAL -> <s> S </s> 
\end{verbatim}
In Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.50]{glue.pdf}
\end{center}
\caption{Affect on model score by changing glue-rule formulation}
\label{fig:glue}
\end{figure}

>>>>

%% Sample file $Id: PBML_article.tex 134 2010-07-01 19:28:04Z popel $
\documentclass{pbml}
%\documentclass[nofonts]{pbml} % for XeLaTeX without Pagella and DejaVu fonts
%\documentclass[color]{pbml} % for color images and hypertext links
% test

@@

Secondly, the glue rule formulation in Moses and cdec is different from Joshua's. In Moses and cdec, the glue rule grammar is:
\begin{verbatim}
   S -> <s>
   S -> S X
   GOAL -> S </s> 
\end{verbatim}
where <s> and </s> are first-class words like any other. In Joshua, the glue rule grammar is:
\begin{verbatim}
   S -> X
   S -> S X
   GOAL -> <s> S </s> 
\end{verbatim}
In the Moses and cdec formulation, glued hypotheses know that they are bound to the beginning of sentence <s>.  Therefore, their left language model state is empty and more hypotheses can recombine.  This is better than Joshua, where hypotheses are informed about <s> and </s> only after forming a complete sentence, so the left states are spuriously ambiguous.  Moreover, hypothesis score estimates are more accurate when they know about <s> earlier. Figure~\ref{fig:glue} shows the improvement in cdec by changing the glue rule formulation. This improvement was the direct result of research comparing the three decoders.

\begin{figure}[h]
\begin{center}
\input{1111-8/glue_model.tex}
\end{center}
\caption{Effect on model score by changing glue-rule formulation}
\label{fig:glue}
\end{figure}
